# Results

<style>
body {
text-align: justify}
</style>

```{r echo=FALSE}
library(ggplot2)
library(readxl)
#install.packages("viridis")
library(viridis)
#ggplot theme
theme_qwen<- function() {
  font <- "serif"
  
  ggplot2::theme(
    
    #Text format:
    #This sets the font, size, type and colour of text for the chart's title
    plot.title = ggplot2::element_text(family=font,
                                       size=26,
                                       face="bold",
                                       color="#2C6975"),
    #This sets the font, size, type and colour of text for the chart's subtitle, as well as setting a margin between the title and the subtitle
    plot.subtitle = ggplot2::element_text(family=font,
                                          size=23,
                                          color = "#0a3c62",
                                          margin=ggplot2::margin(7,0,7,0)),
    plot.caption = ggplot2::element_blank(),
    # plot.caption = ggplot2::element_text(family=font,
    #                                      size=16,
    #                                      face = "bold",
    #                                      color = "#063051",
    #                                      margin=ggplot2::margin(7,50,7,15)),
    #This leaves the caption text element empty, because it is set elsewhere in the finalise plot function
    
    #Legend format
    #This sets the position and alignment of the legend, removes a title and backround for it and sets the requirements for any text within the legend. The legend may often need some more manual tweaking when it comes to its exact position based on the plot coordinates.
    legend.position = "top",
    legend.text.align = 0,
    legend.background = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.key = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(family=font,
                                        size=16,
                                        face = "bold",
                                        color="#2C6975"),
    
    #Axis format
    #This sets the text font, size and colour for the axis test, as well as setting the margins and removes lines and ticks.
    #In some cases, axis lines and axis ticks are things we would want to have in the chart - the cookbook shows examples of how to do so.
    axis.title = element_text(family=font, size = 18, face = "bold", color="#2C6975"),
    axis.text = element_text(family=font, size = 16, face = "bold", color="#2C6975"),
    axis.text.x = ggplot2::element_text(margin=ggplot2::margin(5, b = 10), family=font, color="#2C6975"),
    axis.ticks = ggplot2::element_blank(),
    axis.line = element_line(color = "#E9765B", arrow = arrow(length = unit(0.6, "lines"), type = "closed")),
    #Grid lines
    #This removes all minor gridlines and adds major y gridlines. In many cases you will want to change this to remove y gridlines and add x gridlines. The cookbook shows you examples for doing so
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_line(color="#a9b7be"),
    panel.grid.major.x = ggplot2::element_line(color="#a9b7be"),
    panel.border = element_blank(),
    #Blank background
    panel.background = element_rect(fill = "#F5F5F0",
                                    size = 2),
    #This sets the panel background as blank, removing the standard grey ggplot background colour from the plot
    
    #Strip background (#This sets the panel background for facet-wrapped plots to white, removing the standard grey ggplot background colour and sets the title size of the facet-wrap title to font size 22)
    strip.background = element_rect(fill = "#2C6975", color = "#2C6975"),
    strip.text = element_text(size = rel(1), face = "bold", color = "white")
  )
}
```

```{r include=FALSE}
# Systemic antibody response

Systemic_mono <- readxl::read_xlsx(path = "Systemic antibody response to vaccines.xlsx", 
                                   sheet = "Monovalent") 
Mucosal_mono <- readxl::read_xlsx(path = "Mucosal antibody response to vaccines.xlsx",
                                  sheet = "Monovalent")
Systemic_biva <- readxl::read_xlsx(path = "Systemic antibody response to vaccines.xlsx",
                                   sheet = "Bivalent") 
Mucosal_biva <- readxl::read_xlsx(path = "Mucosal antibody response to vaccines.xlsx",
                     sheet = "Bivalent")

Systemic_mono$Treatment <- as.factor(Systemic_mono$Treatment)
Mucosal_mono$Treatment <- as.factor(Mucosal_mono$Treatment)
Systemic_biva$Treatment <- as.factor(Systemic_biva$Treatment)
Mucosal_biva$Treatment <- as.factor(Mucosal_biva$Treatment)
```

## Systemic antibody response


### Monovalent vaccines

```{r, fig.height=11, fig.width=16, fig.cap="Systemic antibody response (IgM) to monovalent vaccines", echo=FALSE}
# head(Systemic_mono)
# levels(Systemic_mono$Treatment)
ggplot(Systemic_mono, aes(x=Day_post_vaccination, y = OD_450_nm, color=Treatment))+
  geom_point(size=3)+theme_qwen()+ggtitle("Systemic antibody response (IgM) to monovalent vaccines")+
  scale_color_viridis(discrete=TRUE, option="viridis")

```

### Bivalent vaccines

```{r, fig.height=11, fig.width=16, fig.cap="Systemic antibody response (IgM) to bivalent vaccines", echo=FALSE}
# head(Systemic_biva)
# levels(Systemic_biva$Treatment)
ggplot(Systemic_biva, aes(x=Day_post_vaccination, y = OD_450_nm, colour=Treatment))+
  geom_point(size=3)+theme_qwen()+ggtitle("Systemic antibody response (IgM) to bivalent vaccines")+
  scale_color_viridis(discrete=TRUE, option="viridis")
```

## Mucosal antibody response

### Monovalent vaccines

```{r, fig.height=11, fig.width=16, fig.cap="Mucosal antibody response (IgM) to monovalent vaccines", echo=FALSE}
# head(Mucosal_mono)
# levels(Mucosal_mono$Treatment)
ggplot(Mucosal_mono, aes(x=Day_post_vaccination, y = OD_450_nm, colour=Treatment))+
  geom_point(size=3)+theme_qwen()+ggtitle("Mucosal antibody response (IgM) to monovalent vaccines")+
  scale_color_viridis(discrete=TRUE, option="viridis")
```

### Bivalent vaccines

```{r, fig.height=11, fig.width=16, fig.cap="Mucosal antibody response (IgM) to monovalent vaccines", echo=FALSE}
# head(Mucosal_biva)
# levels(Mucosal_biva$Treatment)
ggplot(Mucosal_biva, aes(x=Day_post_vaccination, y = OD_450_nm, colour=Treatment))+
  geom_point(size=3)+theme_qwen()+ggtitle("Mucosal antibody response (IgM) to monovalent vaccines")+
  scale_color_viridis(discrete=TRUE, option="viridis")
```

## Challenge test 1 (Single group)

```{r include=FALSE}
# Bacterial challenges
Challenge1 <- readxl::read_xlsx(path = "Bacterial challenge.xlsx", sheet = "Challenge 1")
Challenge1$Group <- as.factor(Challenge1$Group)
Challenge1$Challenge <- as.factor(Challenge1$Challenge)
Challenge1$Aquarium_number <- as.factor(Challenge1$Aquarium_number)
```

### Relative percentage survival (single dose) 

```{r, fig.height=11, fig.width=16, fig.cap="Survival rates of samples of 20 fish Nile tilapia challenged 4 weeks after immunization with a single vaccine dose or with a control (PBS)", echo=FALSE}

```


## Challenge test 2 (Booster group)

```{r include=FALSE}
Challenge2 <- readxl::read_xlsx(path = "Bacterial challenge.xlsx", sheet = "Challenge 2")
Challenge2$Group <- as.factor(Challenge2$Group)
Challenge2$Challenge <- as.factor(Challenge2$Challenge)
Challenge2$Aquarium_number <- as.factor(Challenge2$Aquarium_number)
```

### Relative percentage survival (booster)

```{r, fig.height=11, fig.width=16, fig.cap="Survival rates of samples of 20 fish Nile tilapia challenged 12 weeks after immunization with two vaccine doses (primary + booster) or with a control (PBS)", echo=FALSE}
```

### Kaplan-Meier survival estimates for challenge test 1

```{r include=FALSE}
#install.packages(c("survival", "survminer"))
library("survival")
library("survminer")

```

#### Monovalent versus bivalent formulations  {-}

```{r echo=FALSE, fig.height=12, fig.width=16, fig.cap="Survival curves using the combination of multiple factors. 20 fish Nile tilapia were challenged 4 weeks after immunization with a single vaccine dose or with a control (PBS)",}
challenge1_KM <- readxl::read_xlsx(path = "Bacterial challenge.xlsx", sheet = "Challenge 1 KM")

challenge1_KM$treatment <- as.factor(challenge1_KM$treatment)
challenge1_KM$vaccine <- as.factor(challenge1_KM$vaccine)
challenge1_KM$type <- as.factor(challenge1_KM$type)


fitchallenge1 <- survfit( Surv(time, status) ~ vaccine + treatment + type,
                          data = challenge1_KM )
ggsurv1 <- ggsurvplot(fitchallenge1, fun = "event", conf.int = TRUE,
                     ggtheme = theme_qwen())

ggsurv1$plot +theme_qwen() + theme(legend.position = "bottom",
         legend.text = element_text(size=9,
                                    face = "bold",
                                    color="#2C6975")
         )+facet_grid(treatment ~ type)+theme(strip.text.y = element_text(margin = margin(0.5,0,0.5,0, "cm")))+
  xlab("Hours post-infection")
```

### Kaplan-Meier survival estimates for challenge test 2

```{r}

```

#### Monovalent versus bivalent formulations  {-}

```{r}

```



# Discussion